Data Cleaning

### 2025-12-08 Data Cleaning.Rmd
Added notes on classification models to try.
Added code to pull dose from previous year.

>>>>

# do regression tree
# LDA/QDA
# random forest

# Look at performance of a model that simply pulls previous year dose

closest_prev_dose <- df_lag_incdec |>
  rowwise() |>
  mutate(
    target_time = Timestamp - years(1),
    prev_year_dose = df_lag_incdec$value[which.min(abs(df_lag_incdec$Timestamp - target_time))]
  ) |>
  ungroup()

closest_prev_dose
